\section{Future Work}

The static mapper currently incorporates the various noise by reducing the update values in the map. 
A possible improvement to the weighting could be considering the entire covariance matrix instead of the individual standard deviation. 
Using the noise more proactive could also improve the mapping results and should help converging faster towards the correct result.
Seen as the localization noise is a significant influence on the mapping any improvement in the accuracy would also benefit the mapping.


The learner showed unbalanced learning of the two transition probabilities.
It is believed that the origins of these problems stems from the static mapping. 
A mapping method that more accurately incorporates the noise could help solve this challenge. 


The classification for converting the dynamics into maps for the localization was handled by a manually designed classifier.
By obtaining vast amounts of data it might be possible to improve the classification through machine learning techniques. 


To continue the development of the Dynamic mapping system it would be beneficial to evaluate the long term performance of the system. 
This should investigate the long-term effects of the feedback between the localization and the dynamic mapping.



\subsection{future notes}

Precise mapping of static environment by incorporation of sensor and localization noise
Separation of sensor and localisation noise?
Used aktively instead of just towards unknown?
Use of feedback from further on, maybe a blueprint map
Brug principle component scores af covariance istedet for bare summen af std afvigelser i reduced ideal inverse sensor model. Det andet underestimate ved kun at se på projektionerne ind i akserne. Muligvis kan determinanten(arealet i en standard afvigelses konfidens elipse.)
Korrekt Indkorporering af sensorstøj burde resultere i hurtigere convergering mod korrekt kort. Sådan en burde laves.
2. Long-term fast adaptive map representation of dynamic environments

3. Improved localization with a continuously adapted map of good features
The classification
More data -> better classification
Machine learning techniques?

A better use (future work)
Localization -> use more values
Planner -> balancing the the cost


4. Integration and evaluation on the MiR-100 platform
Evaluation methods
Evaluation only for hours, but a large scale evaluation in industrial for weeks is required to show long term adaptation to changes and learning real obstacles dynamic

